---
title: "In-class Exercise 5"
author: "Tasaporn Visawameteekul"
date: 11 February 2023
date-modified: "`r Sys.Date()`"
execute: 
  echo: true
  eval: true
  warning: false
format: html
toc: true
editor: visual
---

Getting Started

# Install and launching R packages

Two packages will be installed and loaded. They are: tidyverse, ggiraph

```{r}
pacman::p_load(corrplot, tidyverse, ggstatsplot)
```

Read data

```{r, warning=FALSE, message = FALSE}
wine <- read_csv("data/wine_quality.csv")
glimpse(wine)
```

```{r}
pairs(wine[,1:11])
```

```{r}
pairs(wine[,2:12])
```

Drawing the lower corner

```{r}
pairs(wine[,2:12], upper.panel = NULL)
```

display on upper

```{r}
pairs(wine[,2:12], lower.panel = NULL)
```

## [ggcorrmat](https://www.rdocumentation.org/packages/ggstatsplot/versions/0.2.0/topics/ggcorrmat)

Visualization of a correlation matrix. The message below x = ... explain the significant level.
We also have an option to resize the cross according to the significant level.

```{r}
ggstatsplot::ggcorrmat(
  data = wine, 
  cor.vars = 1:11)
```

```{r}
ggstatsplot::ggcorrmat(
  data = wine, 
  cor.vars = 1:11,
  ggcorrplot.args = list(outline.color = "black", 
                         hc.order = TRUE,
                         tl.cex = 10),
  title    = "Correlogram for wine dataset",
  subtitle = "Four pairs are no significant at p < 0.05"
)
```

Include correlation coefficient

## Correlation plot

Corrplot is not a ggplot extension but based on Rgraphic

ggcorrplot will require the object .corr which can be generated with the command cor.

```{r}
wine.cor <- cor(wine[, 1:11])
corrplot(wine.cor)
```

Correlogram

The slimmer one represents highly correlate relationship.

```{r}
corrplot(wine.cor, 
         method = "ellipse") 
```

```{r}
corrplot(wine.cor, 
         method = "ellipse", 
         type="lower")
```

corrplot.mixed allows us to combine the corrplot and the corrmat.

```{r}
corrplot.mixed(wine.cor, 
               lower = "ellipse", 
               upper = "number",
               tl.pos = "lt",
               diag = "l",
               tl.col = "blue")
```
