---
title: "In-class Exercise 8"
author: "Tasaporn Visawameteekul"
date: 11 March 2023
date-modified: "`r Sys.Date()`"
execute: 
  echo: true
  eval: true
  warning: false
format: html
toc: true
editor: visual
---

# Lesson9: **Information Dashboard Design: R methods**

## Lecture

-   Don't put everything on dashboard. We should be selective
-   There are different types of dashboard. Typically categorized into 3 groups
    -   Operation dashboard - operation centric
    -   Strategic dashboard
    -   Analytics dashboard

We can set up the visualize workshop to gather the requirement and show the use case to the user.

We are not using the show case from the same industry but instead show other industry so that they don't limit themselves to the visual existing in that domain.

Then in the next step we can focus on the use case from the same industry and gather the data they have.

Make it the iteration that you involve the client in the process.

We try to work on the separate plot and get the feedback from the user part by part.

## Hands-on

```{r}
# pacman::p_load(lubridate, ggthemes, reactable,
# reactablefmtr, gt, gtExtras, tidyverse)
```

```{r}
# library(RODBC)
# con <- odbcConnectAccess('data/Coffee Chain.mdb')
# coffeechain <- sqlFetch(con, 'CoffeeChain Query')
# write_rds(coffeechain, "data/CoffeeChain.rds")
# odbcClose(con)
```

```{r}
# coffeechain <- read_rds("data/CoffeeChain.rds")
```

```{r}
# product <- coffeechain %>%
#   group_by(`Product`) %>%
#   summarise(`target` = sum(`Budget Sales`),
#             `current` = sum(`Sales`)) %>%
#   ungroup()
```

```{r}
# ggplot(product, aes(Product, current)) + 
#   geom_col(aes(Product, max(target) * 1.01),
#            fill="grey85", width=0.85) +
#   geom_col(aes(Product, target * 0.75),
#            fill="grey60", width=0.85) +
#   geom_col(aes(Product, target * 0.5),
#            fill="grey50", width=0.85) +
#   geom_col(aes(Product, current), 
#            width=0.35,
#            fill = "black") + 
#   geom_errorbar(aes(y = target,
#                     x = Product, 
#                     ymin = target,
#                     ymax= target), 
#                 width = .4,
#                 colour = "red",
#                 size = 1) +
#   coord_flip()
```

```{r}
# sales_report <- coffeechain %>%
#   filter(Date >= "2013-01-01") %>%
#   mutate(Month = month(Date)) %>%
#   group_by(Month, Product) %>%
#   summarise(Sales = sum(Sales)) %>%
#   ungroup() %>%
#   select(Month, Product, Sales)
```

```{r}
# mins <- group_by(sales_report, Product) %>% 
#   slice(which.min(Sales))
# maxs <- group_by(sales_report, Product) %>% 
#   slice(which.max(Sales))
# ends <- group_by(sales_report, Product) %>% 
#   filter(Month == max(Month))
```

```{r}
# quarts <- sales_report %>%
#   group_by(Product) %>%
#   summarise(quart1 = quantile(Sales, 
#                               0.25),
#             quart2 = quantile(Sales, 
#                               0.75)) %>%
#   right_join(sales_report)
```

```{r}
# report <- coffeechain %>%
#   mutate(Year = year(Date)) %>%
#   filter(Year == "2013") %>%
#   mutate (Month = month(Date, 
#                         label = TRUE, 
#                         abbr = TRUE)) %>%
#   group_by(Product, Month) %>%
#   summarise(Sales = sum(Sales)) %>%
#   ungroup()
```

```{r}

```
