---
title: "Take-home Exercise 4"
subtitle: "Putting Visual Analytics into Practical Use"
author: "Tasaporn Visawameteekul"
date: "16 Feb 2023"
affiliation: "SMU MITB"
format: 
  html:
    mainfont: system-ui
    fontsize: smaller
    code-fold: false
    code-overflow: wrap
    highlight-style: solarized
    page-layout: full
    toc: true
    number-sections: true
    toc_float: 
      collapsed: true
---

# The task

In this take-home exercise, you are required to uncover the impact of COVID-19 as well as the global economic and political dynamic in 2022 on Singapore bi-lateral trade (i.e. Import, Export and Trade Balance) by using appropriate analytical visualisation techniques learned in **Lesson 6: It's About Time**. Students are encouraged to apply appropriate interactive techniques to enhance user and data discovery experiences.

The write-up of the take-home exercise should include but not limited to the followings:

-   Describe the selection and designed consideration of the analytical data visualisation used. The discussion should limit to not more than 150 words each.
-   A reproducible description of the procedures used to prepare the analytical visualisation. Please refer to the peer submission I shared.
-   A write-up of not more than 100 words to discuss the patterns reveal by each analytical visualization prepared.

**Packages**

```{r, results='hide', message=FALSE}
packages = c('readxl', 'datawizard')
for(p in packages){
  if(!require(p,character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

# Data

For the purpose of this take-home exercise, Merchandise Trade provided by Department of Statistics, Singapore (DOS) will be used. The data are available under the sub-section of Merchandise Trade by Region/Market. You should download the data by clicking on the link Download all in Excel on the same webpage. The study period should be between January 2020 to December 2022.

**Checking the number of sheets it contains**

```{r}
excel_sheets("data/data.xlsx")
```

**Importing data**

```{r import, warning=FALSE}
T1 <- data_transpose(read_excel("data/data.xlsx", sheet = "T1"), rownames = "Month", colnames = TRUE)
T2 <- data_transpose(read_excel("data/data.xlsx", sheet = "T2"), rownames = "Month", colnames = TRUE)
```

## T1 table: Merchandise Imports By Region/Market, Monthly

```{r T1, message=FALSE}
#| code-fold: true
knitr::kable(
  head(T1, 5))
```

## T2 table: Merchandise Exports By Region/Market, Monthly

```{r T2, message=FALSE}
#| code-fold: true
knitr::kable(
  head(T2, 5))
```
